---
title: "CaseStudyHighlandsCafe"
author: "Alde"
date: "7/30/2021"
output: html_document
---

I am going to analyse data that I was received from my lecturer while I was studying Business Analysis course at the university.

##Stage 1: Firstly Install required packages.
```{r reading packages}
install.packages("tidyverse")
install.packages("ggplot2")
install.packages("janitor")

library(tidyverse)
library(ggplot2)
library(janitor)
```

##Stage 2: loading datasets

```{r assigning dataset}
jan_sales <- read_csv('/Users/alde/OneDrive/A.OD. Learning/capstone/CaseStudy/Highlands_Sales_Jan.csv')
```

Stage 3: checking and cleaning data

```{r view column names}
colnames(jan_sales)
```


Because the column names in he tables have unnecessary spaces, this stage is to clean them using clean_nam() functions

```{r clean table column names}

jan_sales <- clean_names(jan_sales)

```

Check the column names again
```{r gimpse the table}
glimpse(jan_sales)

```

After cleaning the column names, it is the time to fill missing columns.

##Stage 4: correcting the gaps

This stage includes calculation for data to be put under column: 'Spending on drinks', 'Spending of foods' and 'total spending

```{r calculating empty columns}
 a <- jan_sales
  a$`spending_on_drinks` <- (a$`drinks_orders`*a$`drinks_price`)
  a$`spending_of_foods` <- (a$`foods_orders`*a$`foods_price`)
  a$`total_spending` <- a$`spending_on_drinks`+a$`spending_of_foods`
jan_sales <- a
 # View(jan_sales)
```

```{r check null value in the table}
is.null(jan_sales)
```

this chunk si to check if the number of rows are equal after checking if the table still has any null value by is.null() function

```{r check if there's any null value}
a <- nrow(jan_sales)
b <- sum(count(jan_sales))
 if (a==b)
 {print(TRUE)}
```

It seems that I have carefully cleaned the table,

```{r visulisation test}
ggplot(jan_sales, aes(x=occupation,fill=total_spending))+geom_bar(fill = "blue", colour = "red")
```

##Stage 5: Filtering the table

this will will manipulate the data from the table finding out who is likely to make large payment

```{r bar for occupation vs drinks}
ggplot(jan_sales, aes(x=occupation,fill=total_spending))+geom_bar(colour = "red")+facet_wrap(~gender)
```

```{r bar for male occupation vs drinks}
plot_male <- filter(jan_sales, gender=="Male")
ggplot(plot_male, aes(x=occupation,fill=drinks))+geom_bar()
```

```{r for female occupation vs }
plot_female <- filter(jan_sales, gender=="Female")
ggplot(plot_female, aes(x=occupation,fill=drinks))+geom_bar()
```

##Summary

Finding some important information for making report later

Calculate percentage of males ordered drinks but did not order foods

```{r DYFN_Male}
DYFN_Male <- nrow(filter(jan_sales, foods_orders==0 ))/nrow(jan_sales)
print(paste0("Percentage of males ordered drinks but did not order foods is ", DYFN_Male*100,"%"))
```

the coding will also print the full text to answer the question as "Percentage of males ordered drinks but did not order foods is 38.8%"

Calculate percentage of Highlands female customers

```{r % of female customers}
print(paste0("Percentage of Highlands female customers is ", (nrow(filter(jan_sales,gender=="Female"))/nrow(jan_sales))*100," %"))
```




