---
title: "R Notebook"
output: html_notebook
---

---
title: "CaseStudyHighlandsCafe"
author: "Alde"
date: "7/30/2021"
output: html_document
---

I am going to analyse data that I was received from my lecturer while I was studying Business Analysis course at the university.

Stage 1: Firstly Install required packages.
```{r reading packages}
install.packages("tidyverse")
install.packages("ggplot2")
install.packages("janitor")

library(tidyverse)
library(ggplot2)
library(janitor)
```

Stage 2: loading datasets

```{r}
jan_sales <- read_csv('/Users/alde/OneDrive/A.OD. Learning/capstone/CaseStudy/Highlands_Sales_Jan.csv')
feb_sales <- read_csv('/Users/alde/OneDrive/A.OD. Learning/capstone/CaseStudy/Highlands_Sales_Feb.csv')
mar_sales <- read_csv('/Users/alde/OneDrive/A.OD. Learning/capstone/CaseStudy/Highlands_Sales_Mar.csv')
apr_sales <- read_csv('/Users/alde/OneDrive/A.OD. Learning/capstone/CaseStudy/Highlands_Sales_Apr.csv')
may_sales <- read_csv('/Users/alde/OneDrive/A.OD. Learning/capstone/CaseStudy/Highlands_Sales_May.csv')
jun_sales <- read_csv('/Users/alde/OneDrive/A.OD. Learning/capstone/CaseStudy/Highlands_Sales_Jun.csv')
jul_sales <- read_csv('/Users/alde/OneDrive/A.OD. Learning/capstone/CaseStudy/Highlands_Sales_Jul.csv')
aug_sales <- read_csv('/Users/alde/OneDrive/A.OD. Learning/capstone/CaseStudy/Highlands_Sales_Aug.csv')
sept_sales <- read_csv('/Users/alde/OneDrive/A.OD. Learning/capstone/CaseStudy/Highlands_Sales_Sept.csv')
oct_sales <- read_csv('/Users/alde/OneDrive/A.OD. Learning/capstone/CaseStudy/Highlands_Sales_Oct.csv')
nov_sales <- read_csv('/Users/alde/OneDrive/A.OD. Learning/capstone/CaseStudy/Highlands_Sales_Nov.csv')
dec_sales <- read_csv('/Users/alde/OneDrive/A.OD. Learning/capstone/CaseStudy/Highlands_Sales_Dec.csv')


```

Stage 3: Because the column names in he tables have unnecessary spaces, this stage is to clean them using clean_nam() functions

```{r clean table column names}

jan_sales <- clean_names(jan_sales)
feb_sales <- clean_names(feb_sales)
mar_sales <- clean_names(mar_sales)
apr_sales <- clean_names(apr_sales)
may_sales <- clean_names(may_sales)
jun_sales <- clean_names(jun_sales)
jul_sales <- clean_names(jul_sales)
aug_sales <- clean_names(aug_sales)
sept_sales <- clean_names(sept_sales)
oct_sales <- clean_names(oct_sales)
nov_sales <- clean_names(nov_sales)
dec_sales <- clean_names(dec_sales)

```


Check the column names
```{r}
glimpse(jan_sales)

```

After cleaning the column names, it is the time to tada

This stage includes calculation for data to be put under column: 'Spending on drinks', 'Spending of foods' and 'total spending

```{r}
 a <- jan_sales
  a$`spending_on_drinks` <- (a$`drinks_orders`*a$`drinks_price`)
  a$`spending_of_foods` <- (a$`foods_orders`*a$`foods_price`)
  a$`total_spending` <- a$`spending_on_drinks`+a$`spending_of_foods`
jan_sales <- a
  View(jan_sales)
```




